My title

### 2024-02-12 paper/paper.qmd
Figure 1 basically replicated

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Aaron Liu
  - Jimmy Luc
  - Maroosh Gillani
thanks: "Code and data are available at: https://github.com/rex009x/us_birth_rates/tree/master/data . A replication of various aspects in this paper are available at: LINK ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
# workplace setup

@@

# replicate figure 1 from the original paper
fig_1_data %>% ggplot(aes(x = year, y = brate_all)) +
  geom_line(color = "blue") +
  labs(x = "Year", y = "Births per 1,000 women age 15–44")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Maroosh Gillani
  - Aaron Liu
  - Jimmy Luc
thanks: "Code and data are available at: https://github.com/rex009x/us_birth_rates/tree/master/data . A replication of various aspects in this paper are available at: LINK ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
```{r, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
# workplace setup

@@

# replicate figure 1 from the original paper
fig_1_data %>% ggplot(aes(x = year, y = brate_all)) +
  geom_line(color = "#378bd4", size = 1) +
  labs(x = "Year", y = "Births per 1,000 women age 15–44") +
  scale_y_continuous(limits = c(50,80), breaks = seq(50, 80, by = 5)) +
  scale_x_continuous(limits = c(1980,2020), breaks = seq(1980, 2020, by = 5)) +
  theme_classic()
```
